---
title: "ipsci"
author: "Jai Jeffryes, Tamiko Jenkins, Nicholas Chung"
date: "11/22/2019"
output: 
  html_document:
    code_folding: hide
    highlight: pygments
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, message=FALSE}
# Packages used in the ingestion of data
library(httr)         # Wrapper for the curl package
library(XML)          # Dealing with text in xml
library(jsonlite)     # Getting and formatting JSON 
library(rplos)        # API to PLOS for journals
library(readr)        # Reading rectangular data
library(plyr)         # Wrangling data
library(dplyr)        # Wrangling data
library(tibble)       # Tidier table object
library(tidyr)        # Tidying data
library(stringr)      # Manipulating strings using RegEx
library(purrr)
library(tm)           # Text mining
library(rjson)        # Work with JSON format
library(fulltext)     # Text mining of open access journals

# Packages used for special use cases
library(stats)
library(topicmodels)  # for LDA topic modelling 
library(SnowballC)    # for stemming
library(tidyverse)    # general utility & workflow functions 
library(tidytext)     # text analysis in R 
library(lubridate)    # working with times and dates   
library(rvest)        # Download and manipulate HTML

# Packages used to prettify and produce visualizations
library(kableExtra)   #
library(rjson)        # Work with JSON format
library(ggplot2)      # graphs library
library(purrr)        #
library(cowplot)      # ggplot2 add-on for pretty graphs
```

## Proposal
Assessment of the state of science is a requirement for research. Assessment of intellectual property is a requirement for
capitalization of knowledge for profit. This project explores tools for surveying patent data and research data in order to develop
methods for making these assessments.
 
The project begins with an examination of data from NASA, whose open data portal includes a dataset of NASA patents. The format is a
delimited text file. The data include a patent case number and title. Exploration of this dataset may include unsupervised learning
to yield topics of patents.
 
The World Intellectual Property Organization (WIPO) publishes The WIPO Manual on Open Source Patent Analytics with instruction for data
interrogation useful for subsequent parts of this project. The project will continue with a more detailed exploration of patent cases opened
by NASA or another science-focused organization with a view to revealing more topics from within patent case data other than the title of the case, perhaps from the patent application, for example.
 
There are at least two data sources for patent data. The primary data source is the U.S. Patent and Trademark Office (USPTO), whose Open
Data Portal publishes many datasets in various formats. USPTO also supplies APIs for patent data retrieval. Besides these APIs, there is
at least one potentially useful third party API called PatentsView.
 
One resource for research publications is the Public Library of Science (PLOS), who publish open access peer reviewed articles. The
inventory of articles seems limited, but appears to enable an introduction to searching for research papers for which we will utilize the R package, `rplos`, a programmatic interface to the Solr based search API provided by PLOS. Solr is an open source search platform built on
Apache Lucerne.

Our research topic is quantification and characterization of NASA innovation through inspection of NASA's patents. For example, we expect to count patents which cite NASA patents (quantification) and to mine topics from NASA patents (characterization). We will report and visualize these findings.

The motivation for this project relates to methods for Information Retrieval and the team’s collective interest and experience in startup and scientific industries. Efficient topic modelling can form the foundation of a number of advanced NLP techniques such as Word sense disambiguation, Natural Text Generation, and automatic Summarization on its own. A number of derivative analysis are possible based on NLP, including studies combining our results with industry or innovation metrics.

## NASA Patents
- Data source: [NASA's Open Data Portal](https://data.nasa.gov/Raw-Data/NASA-Patents/gquh-watm). Includes column specification.
- File: NASA_Patents.csv
- Download date: 11/14/2019

### Data preparation notes
- Once you determine the data types of your columns,set the specifications and then use them for reading.
- [`readr` blog post](https://blog.rstudio.com/2016/08/05/readr-1-0-0/). Illustrates the approach, although this syntax doesn't work anymore. The approach writes the specification to a file.
- [readr - how to update col_spec object from spec()](https://stackoverflow.com/questions/39135129/readr-how-to-update-col-spec-object-from-spec). Greg H.'s answer on Stack Overflow doesn't require writing to a file. We use this approach. 

```{r nasa}
nasa_patents_fn <- "NASA_Patents.csv"

# Specify datatypes.
nasa_spec <- spec_csv(file = file.path("data", nasa_patents_fn))
nasa_spec$cols[["Status"]] <- col_factor()
nasa_spec$cols[["Patent Expiration Date"]] <- col_date("%m/%d/%Y")

# Read patent file.
nasa_patents <- readr::read_csv(file = file.path("data", nasa_patents_fn),
                                col_types = nasa_spec)

# In variable names, replace spaces.
names(nasa_patents) <- str_replace_all(string = names(nasa_patents),
                                       pattern = " ",
                                       replacement = "_")

# Transform the application number to USPTO format
nasa_patents <- nasa_patents %>%
  mutate(Application_SN_uspto = str_c("US",
        str_replace_all(Application_SN, "[[:punct:]]", "")))
```

## Retrieve USPTO patent data
```{r get_uspto_patent}
# Example https://developer.uspto.gov/ibd-api/v1/patent/application?applicationNumber=US12795356'
is_na_patnum <- is.na(nasa_patents$Patent_Number)
is_patnum <- nasa_patents$Patent_Number > 0
nasa_patent_numbers <- nasa_patents$Patent_Number[!is_na_patnum & is_patnum]

# Need to review contents of JSON files.
for (app in nasa_patents$Application_SN_uspto) {
  #get_patent_application_uspto(app)
  url <- paste0('https://developer.uspto.gov/ibd-api/v1/patent/application?applicationNumber=',app)
  path <- "data/uspto"
  file_path <- file.path(path, str_c(app, ".html"))

  if (!file.exists(file_path)) {
    patent_application <- jsonlite::fromJSON(url)
    #test
    print(patent_application)
    #  Bulk download not ideal
    ##download.file(patent_application$response$docs$archiveUrl, file.path(path)) 
    #  Instead use the following form to query for new HTML files 
    #  http://patft.uspto.gov/netahtml/PTO/index.html
    break
  }
}

print("Downloads complete.")
```

### select relevant patent data from Google HTML
Exploratory chunk disabled.
```{r, eval=FALSE}
# explore downloaded data
raw.html <- read_html("data/6020587.html")
# title
raw.html %>% html_nodes("body search-app article h1") %>% html_text() %>% .[[1]]
# filing date
raw.html %>% html_nodes("[itemprop='filingDate']") %>% html_text() %>% .[[2]]
# abstract
raw.html %>% html_nodes("abstract") %>% html_text()
# description > origin of the invention
raw.html %>% html_nodes("body search-app article section div div p") %>% html_text() %>% .[[1]]
# description > background of the invention > field of the invention
raw.html %>% html_nodes("body search-app article section div div p") %>% html_text() %>% .[[3]]
# cited by 
raw.html %>% html_nodes(xpath="/html/body/search-app/article/table") %>% html_table()
# cited by (count) nrow()
cited_by <- raw.html %>% html_nodes(xpath="/html/body/search-app/article/table") %>% html_table() 
# patent citations 
raw.html %>% html_nodes(xpath="/html/body/search-app/article/section/table") %>% html_table()
raw.html %>% html_nodes(xpath="/html/body/search-app/article/section/h2") %>% html_text()
```

### clean and transform selected data into dataframe
```{r}
# create object with all filenames
files <- list.files(path="data", pattern="[0-9]{5,}.html", full.names=TRUE, recursive=FALSE)

# create lists of extracted data
# title
raw.title <- lapply(files, function(x) {
  raw.html <- read_html(x, header=TRUE) # load file
  # apply function
  raw.html %>% html_nodes("body search-app article h1") %>% html_text() %>% .[[1]] %>% str_remove(" \\n +\\- [[:alpha:]]{6,} [[:alpha:]]{6,}")
})
# abstract
raw.abstract <- lapply(files, function(x) {
  raw.html <- read_html(x, header=TRUE) # load file
  # apply function
  raw.html %>% html_nodes("abstract") %>% html_text()
})
# prior art date as proxy for filing date that includes support 1899 example
filing.date <- lapply(files, function(x) {
  raw.html <- read_html(x, header=TRUE) # load file
  # apply function
  raw.html %>% html_nodes("[itemprop='priorArtDate']") %>% html_text() %>% .[[1]]
})
# description > origin of the invention
raw.origin <- lapply(files, function(x) {
  raw.html <- read_html(x, header=TRUE) # load file
  # apply function
  raw.html %>% html_nodes("body search-app article section div div p") %>% html_text() %>% .[[1]]
})
# description > background of the invention > field of the invention
raw.background <- lapply(files, function(x) {
  raw.html <- read_html(x, header=TRUE) # load file
  # apply function
  raw.html %>% html_nodes("body search-app article section div div p") %>% html_text() %>% .[[3]]
})
```

### section to answer question, "how many other patents does a patent reference ('count.citations'), and how many other patents reference it ('count.cited_by')?" This question is a analagous to, "how many shoulders does a given patent stand on?"
# todo: make sure it works across all dataframes; try incorporating Tommy's snippet

We observe that each patent includes citations to reference other patents, as well as those other patents that cite it. We then ask if it might be possible to identify counts of each to demonstrate, for instance, the count of citations over time

This analysis will help us begin to answer the question, "how, and to what extent, do patents build on other patents?" Subsequent analysis should account for patent density across time, as well as the calculation of a rough proxy metric of the referenciblity of each patent (how much more or less is a given patent cited?).

```{r}
# cited by (count) 
cited_by <- lapply(files, function(x) {
  raw.html <- read_html(x, header=TRUE) # load file
  # apply function
  raw.html %>% html_nodes(xpath="/html/body/search-app/article/section/h2") %>% html_text() %>% str_subset(pattern = "Cited")
})

# clean output
cited_by <- as.character(cited_by)

# cited by (count) 
count.cited_by <- lapply(cited_by, function(x) 
  # remove up to digit
  x %>% str_remove("\\D+")
)
count.cited_by <- lapply(count.cited_by, function(x) 
  # remove after digit
  x %>% str_remove("\\)$")
)

count.cited_by <- lapply(count.cited_by, function(x) 
  # remove after digit
  x %>% as.integer()
)

# citations (count) 
citations <- lapply(files, function(x) {
  raw.html <- read_html(x, header=TRUE) # load file
  # apply function
  raw.html %>% html_nodes(xpath="/html/body/search-app/article/section/h2") %>% html_text() %>% str_subset(pattern = "Patent Citations")
})

# drop Non-Patent Citations
citations <- lapply(citations, function(x) {
  # apply function
  str_detect(x, "Non-") %>%
                  discard(x, .)
})

# clean output
citations <- as.character(citations)

# cited by (count) 
count.citations <- lapply(citations, function(x) 
  # remove up to digit
  x %>% str_remove("\\D+")
)
count.citations <- lapply(count.citations, function(x) 
  # remove after digit
  x %>% str_remove("\\)$")
)

count.citations <- lapply(count.citations, function(x) 
  # remove after digit
  x %>% as.integer()
)
```

### clean text and output to df
```{r}
# not necessary, but makes lists nicer to read
raw.title <- unlist(raw.title, recursive = FALSE)
raw.abstract <- unlist(raw.abstract, recursive = FALSE)
raw.origin <- unlist(raw.origin, recursive = FALSE)
filing.date <- filing.date %>% unlist(recursive = FALSE)
raw.background <- unlist(raw.background, recursive = FALSE)
count.citations <- count.citations %>% unlist(recursive = FALSE)
count.cited_by <- count.cited_by %>% unlist(recursive = FALSE)

# get "appId" with regex
app_num <- unlist(str_extract_all(raw.title, "[A-Z]{2,}[0-9]{6,}[A-Z]+[0-9]?"))

# remove "appId" from "title" 
raw.title <- str_remove(raw.title, app_num)
raw.title <- str_remove(raw.title, " - ") 

# bind lists into dataframe and name columns
raw.df <- setNames(do.call(rbind.data.frame, Map('c', app_num, raw.title, raw.abstract, raw.origin, raw.background, count.cited_by, count.citations, filing.date)), c("appId", "title", "abstract", "origin", "background", "citedBy", "citations", "filingDate"))
head(raw.df, 5)
```

### write to file for easy access
```{r, eval=TRUE}
write.csv(raw.df,"data/patent_text.csv", row.names = FALSE)
```

### EDA and data transformation for visualization
```{r}
raw.df$filingDate <- as.Date(raw.df$filingDate, format = "%Y-%m-%d")

# drop outlier date 
raw.df <- raw.df %>% 
  subset(filingDate != as.Date("1891-12-08"))

# date quartiles 
quartile <- (max(raw.df$filingDate) - min(raw.df$filingDate)) / 4 
q1 <- min(raw.df$filingDate) + quartile
q2 <- min(raw.df$filingDate) + (quartile*2)
q3 <- min(raw.df$filingDate) + (quartile*3)
q4 <- max(raw.df$filingDate)

# citation count per patent filed between 2006 and 2012
citations4 <- raw.df %>% 
  select(citations, citedBy, title, filingDate) %>%
  filter(filingDate >= as.Date(q3) & filingDate <= as.Date(q4))

# citation count per patent filed between 2000 and 2006
citations3 <- raw.df %>% 
  select(citations, citedBy, title, filingDate) %>%
  filter(filingDate >= as.Date(q2) & filingDate <= as.Date(q3))

# citation count per patent filed between 1994 and 2000
citations2 <- raw.df %>% 
  select(citations, citedBy, title, filingDate) %>%
  filter(filingDate >= as.Date(q1) & filingDate <= as.Date(q2))

# citation count per patent filed before 1994
citations1 <- raw.df %>% 
  select(citations, citedBy, title, filingDate) %>%
  filter(filingDate <= as.Date(q1))
```

```{r}
# patent density -- which years most patents?
ggplot(raw.df, aes(x=filingDate)) + 
  geom_histogram(aes(y=..density..), colour="black", fill="white") +
  geom_density(alpha=.2, fill="#FF6666") +
  ggtitle("Patent density by year") +
  xlab("year") + ylab("density")

# citations and citedBy count over all years
c1 <- ggplot(raw.df, aes(x=filingDate, y=citedBy)) + 
  geom_point() +
  ggtitle("(n) cited by other patents by year") +
  xlab("year") + ylab("cited by")
c2 <- ggplot(raw.df, aes(x=filingDate, y=citations)) + 
  geom_point() +
  ggtitle("(n) citations by year") +
  xlab("year") + ylab("citations")
plot_grid(c1, c2, labels = c('A', 'B'), label_size = 12)

# citations count by year quartiles (zoomed in)
p1 <- ggplot(citations1, aes(x=filingDate, y=citations)) + 
  geom_point() +
  #stat_summary(fun.data=mean_cl_normal) + 
  #geom_smooth(method='lm', formula= y~x) +
  ggtitle("(n) citation counts, 2006-2012") +
  xlab("year") + ylab("citations")
p2 <- ggplot(citations2, aes(x=filingDate, y=citations)) + 
  geom_point() +
  ggtitle("(n) citation counts, 2000-2006") +
  xlab("year") + ylab("citations")
p3 <- ggplot(citations3, aes(x=filingDate, y=citations)) + 
  geom_point() +
  ggtitle("(n) citation counts, 1994-2000") +
  xlab("year") + ylab("citations")
p4 <- ggplot(citations4, aes(x=filingDate, y=citations)) + 
  geom_point() +
  ggtitle("(n) citation counts, pre-1994") +
  xlab("year") + ylab("citations")
plot_grid(p1, p2, p3, p4, labels = c('A', 'B', 'C', 'D'), label_size = 12)
```

### read patent text
```{r, eval=TRUE}
raw.df <- read.csv("data/patent_text.csv")
```

# Explore and Transform the Data
Examine the patent text files and view the text sections. We note 932 observations, 8 variables, and 2 integer classes and 6 character classes. 
```{r}
patents <- read.csv("data/patent_text.csv", header = TRUE, stringsAsFactors = FALSE)
glimpse(patents)
kable(head(patents, n=2))
```

## Data integrity
Check to make sure we are not operating on empty data. We are not. 
```{r}
nrow(patents) == sum(complete.cases(patents))
```

Track our documents in case we need to make extra rows for each word
```{r}
#patents <- patents %>%    
  #mutate(docId=as.integer(row.names(.)))
`%notin%` <- Negate(`%in%`)
if('docId' %notin% colnames(.)) patents<-add_column(patents, docId=as.integer(row.names(patents)), .before = 1)
head(patents, n=1)
```
References
1. https://github.com/tidyverse/dplyr/issues/2047
2. https://tibble.tidyverse.org/reference/add_column.html
3. https://www.r-bloggers.com/the-notin-operator/

## String-focused transformations

### Remove third-party additions to text
```{r}
head(patents$title, n=1)
patents <- patents %>%
  #head(n=1) %>%
  mutate(title = str_remove_all(title, " - Google Patents"))
head(patents$title, n=1)
```

### Titles and Abstracts

1. Extract document ids, titles and abstracts and convert to tibble in order to use tidy text methods
2. Replace common European characters into transliterated roman characters (e.g. â is a)
3. Replace upper with lower case characters
4. Tokenize the title and abstract variables into words
5. Remove default English stopword from those words
6. Normalize white-space: Remove leading, trailing and intermediate excess whitespace
7. Remove numbers
Hold off on punctuation (contractions, dashes) and stemming until analysis, and because key terms are more sensitive to these changes
8. We note some words to remove after visualizing the text

```{r} 
patents <- patents %>%
  mutate(title=iconv(title, to='ASCII//TRANSLIT')) %>%
  mutate(title=tolower(title)) %>%
  mutate(title=str_replace_all(title,'\\w*\\d\\w*','')) %>%
  mutate(title=str_replace_all(title,'\\b(apparatus|article|control|device|include.*|provide*|methods*|systems*)\\b','')) %>%
  mutate(abstract=iconv(abstract, to='ASCII//TRANSLIT')) %>%
  mutate(abstract=tolower(abstract)) %>%
  mutate(abstract=str_replace_all(abstract,'\\w*\\d\\w*','')) %>%
  mutate(abstract=str_replace_all(abstract,'\\b(apparatus|article|control|device|include.*|provide.*|methods*|systems*)\\b','')) %>%
  mutate_if(is.character, str_squish)
head(patents, n=2)
```

## Data-focused transformations
 
### Character statistics
```{r}
patents_stats <- patents %>% 
  rowwise() %>% 
  transmute(title = title, title_nchar = nchar(title), title_nmeans= nchar(title),
            abstract=abstract, abstract_nchar = nchar(abstract), abstract_nmeans= nchar(abstract),
            origin = origin, origin_nchar = nchar(origin), origin_nmeans= nchar(origin),
            background = background, background_nchar = nchar(background), background_nmeans= nchar(background)) %>%
  mutate(title_nmeans=colMeans(.[3]), 
         abs_nmeans=colMeans(.[6]), 
         origin_nmeans=colMeans(.[9]), 
         background_nmeans=colMeans(.[12])) %>%
  cbind(select(patents, -c(title, abstract, origin, background)),.)
head(patents_stats, n=2)
```

### Dates
Store the dates in date format yyyy-mm-dd.
```{r}
patents_stats <- patents_stats %>%
  rowwise() %>%
  mutate(filingDate=ymd(filingDate))
head(patents_stats, n=1)
```


## Final Data Definitions
* docId: A unique patent document data record in our sample (NASA)
* appId: A unique patent number 'r'
* citedBy: Other papers citing this paper, provided by Google
* citation: Number of other papers this paper cites
* filingDate: The date the patent was filed in yyyy-mm-dd format (for instance a specific version)
* title: The patent title with the prepended phrase " - Google Patents" removed
* title_nchar [patent_stats]: the number of characters in the title
* title_nmeans [patent_stats]: the average number of characters over all of the titles in all patents
* abstract: a summary of the patent abstract
* abstract_nchar: the number of characters in the abstract
* abstract_nmeans: the average number of characters over all of the abstracts in all patents
* origin: a summary of how the patent originated
* origin_nchar [patent_stats]: the number of characters in the origin
* origin_nmeans [patent_stats]: the average number of characters over all of the origins in all patents
* background: a summary of the patent background
* background_nchar [patent_stats]: the number of characters in the background
* background_nmeans [patent_stats]: the average number of characters over all of the backgrounds in all patents

References:
1. https://dplyr.tidyverse.org/reference/mutate.html#grouped-tibbles
2. https://dplyr.tidyverse.org/reference/summarise.html
3. https://github.com/tidyverse/dplyr/issues/2838
4. https://stackoverflow.com/questions/43897844/r-move-column-to-last-using-dplyr

# Data Analysis
After looking into the patent stats, and transforming the data, we choose title and abstract for our Data Analysis.

## Perform Word Tokenization specific to our type of analysis

### Title word operations
```{r message=FALSE}
tb_titles <- patents %>%
  select(., c(docId, title)) %>%
  as_tibble() %>%
  unnest_tokens(word, title) %>%
  anti_join(stop_words)
```

### Abstract word operations
```{r message=FALSE}
tb_abstracts <- patents %>%
  select(., c(docId, abstract)) %>%
  as_tibble() %>%
  unnest_tokens(word, abstract) %>%
  anti_join(stop_words)
```

## Show Basic Word statistics
1. Note the most frequent words over all patents
2. Note the most frequent words per patent

### Most frequent words in titles
```{r message=FALSE}
title_words <- tb_titles %>%
  count(word, sort = TRUE)

title_words %>%
  top_n(10) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill=word)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  ylab("Word Frequency") +
  ggtitle("Most Common Title Words") 

head(title_words, 5)
```

### Most frequent words in each title
```{r message=FALSE}
title_word_counts <- tb_titles %>%
  count(docId, word, sort = TRUE)%>%
  ungroup()

head(title_word_counts, 5)
```

### Most frequent words in Abstracts
```{r message=FALSE}
abstract_words <- tb_abstracts %>%
  count(word, sort = TRUE)

abstract_words %>%
  top_n(10) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill=word)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  ylab("Word Frequency") +
  ggtitle("Most Common Abstract Words") 

head(abstract_words, 5)
```

### Most frequent words in each Abstract
```{r message=FALSE}
abstract_word_counts <- tb_abstracts %>%
  count(docId, word, sort = TRUE)%>%
  ungroup()

head(abstract_word_counts, 5)
```

References:
1. https://stackoverflow.com/questions/20495598/replace-accented-characters-in-r-with-non-accented-counterpart-utf-8-encoding
2. https://www.tidytextmining.com/tidytext.html

## Cast to Document Term Matrix

### Title DTM
```{r}
title_dtm <- title_word_counts %>%
  cast_dtm(docId, word, n)

title_dtm
```

### Abstract DTM
```{r}
abstract_dtm <- abstract_word_counts %>%
  cast_dtm(docId, word, n)

abstract_dtm
```

## Perform Abstract LDA and Visualize

### Build the LDA
```{r}
# Disable to avoid unintentional overwrites
abstract_lda <- LDA(abstract_dtm, k = 24, control = list(seed = 1234))
abstract_lda
```

```{r}
# Free memory
gc(abstract_dtm)
gc(tb_titles)
gc(tb_abstracts) 
```

### Arrange the LDA and Visualize top words per topic
```{r}
tidy_abstract_lda <- tidy(abstract_lda)

top_abstract_terms <- tidy_abstract_lda %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)
```
 
```{r fig.width=10, fig.height=20}
top_abstract_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  group_by(topic, term) %>%    
  arrange(desc(beta)) %>%  
  ungroup() %>%
  ggplot(aes(term, beta, fill = as.factor(topic))) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  scale_x_reordered() +
  labs(title = "Top 10 terms in each LDA topic",
       x = NULL, y = expression(beta)) +
  facet_wrap(~ topic, ncol = 4, scales = "free")

```

### Review performance of Abstract LDA per document
Our LDA shows an even distribution of probability across many documents. 
```{r message=FALSE}
lda_gamma <- tidy(abstract_lda, matrix = "gamma")

ggplot(lda_gamma, aes(gamma)) +
  geom_histogram() +
  scale_y_log10() +
  labs(title = "Distribution of probabilities for all topics",
       y = "Number of documents", x = expression(gamma))
```

```{r warning=FALSE, message=FALSE, fig.align='center', fig.width=10, fig.height=10}
ggplot(lda_gamma, aes(gamma, fill = as.factor(topic))) +
  geom_histogram(show.legend = FALSE) +
  facet_wrap(~ topic, ncol = 4) +
  scale_y_log10() +
  labs(title = "Distribution of probability for each topic",
       y = "Number of documents", x = expression(gamma))
```

### Experimenting with LDA
Trying another strategy, we can boost the number of topics and then extract the top term per document. Other strategies include creating bi- or tri-grams or combining TF-IDF and other Keywords such as those available in tidytextmining from NASA with the LDA topics or associated words. 

Here we try to increase the topics to 100 (roughly 1/8 of the documents). 
```{r}
gc(abstract_lda)
abstract_lda <- LDA(abstract_dtm, k = 100, control = list(seed = 1234))
abstract_lda
```

### Find the top one term per LDA topic
```{r warning=FALSE, message=FALSE, fig.align='center', fig.width=10, fig.height=10}
topics <- tidy(abstract_lda, matrix = "beta") 
topics %>%  
  mutate(term = reorder(term, beta)) %>% 
  # Need to limit number of terms 
  group_by(term) %>%
  top_n(3, beta) %>%
  ungroup() %>%
  ggplot(aes(term, beta, fill = factor(topic))) +  
  geom_col(show.legend = FALSE) +  
  facet_wrap(~ topic, scales = "free") +  
  labs(x = NULL, y = "Beta") +  
  coord_flip()  
```


```{r}
abs_topics_term <- topics %>%
  group_by(topic) %>% 
  filter(beta == max(beta)) %>% 
  slice(1) %>% 
  ungroup() 
head(abs_topics_term,n=5)
```

### Merge with dataset and extract to csv
Merge and get one topic per document
```{r}
abs_topic_docs <- tidy(abstract_lda, matrix = "gamma")
topics_ <- abs_topic_docs %>% 
  mutate(docId=as.integer(document)) %>%
  select(., -document) %>% 
  group_by(docId) %>% 
  filter(gamma == max(gamma)) %>% 
  slice(1) %>% 
  ungroup()

abs_topic_docs
topics_
```

Get one term per topic
```{r}
terms_ <- subset(abs_topics_term, topic==topics_$docId, -beta) # get subset of relevant attrs 
topic_terms <- inner_join(topics_, terms_, by = "topic") # join subset and df of topic per doc by "topic"
terms_
topic_terms
```

Check for errors
```{r}
# Rewrite
any(is.na(topic_terms))
```

Merge to patent document df
```{r}
patent_topics <- merge(patents, topic_terms, by = "docId") %>% 
  group_by(docId) %>% arrange(., docId)
head(patent_topics)
```

Extract
```{r}
#write.csv(patents_topic_terms,"data/patents_topic_terms.csv")
```

Reference:
1. https://www.tidytextmining.com/tidytext.html
2. https://www.kaggle.com/rtatman/nlp-in-r-topic-modelling#Unsupervised-topic-modeling-with-LDA


## TF-IDF 

Measures the importance of a word within the corpus, potentially surfacing not unique words to the document (tf) but those that are not very frequent in the corpus (IDF). We investigate this potentially more reliable method (given the small dataset (corpus)) until we are able to expand or augment the LDA topic analysis and then test it. 

### Visualize the top TD-IDF words in the corpus
```{r message=FALSE}
abstracts_tf_idf <- tb_abstracts %>% 
  count(docId, word, sort = TRUE) %>%
  ungroup() %>%
  bind_tf_idf(word, docId, n) 

abstracts_tf_idf %>% 
  top_n(10) %>%
  ggplot(aes(word, tf_idf, fill=word)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  ylab("Word TF-IDF") +
  ggtitle("Sample of Most Relevant, Unique Abstract Words in Corpus") 
```

### Find the top one TF-IDF term per document
```{r}
doc_abs_tf_idf <- abstracts_tf_idf %>%
  group_by(docId) %>% 
  filter(tf_idf == max(tf_idf)) %>% 
  slice(1) %>% 
  ungroup() 
head(doc_abs_tf_idf,n=5)
```


### Merge with dataset and extract to csv
Merge
```{r}
doc_terms <- doc_abs_tf_idf %>% transmute(docId=docId, term=word) 
patents_terms <- merge(doc_terms, patents, by='docId')

kable(head(patents_terms, n=2))
```

Extract
```{r}
write.csv(patents_terms,"data/patents_terms.csv")
```

Reference:
1. https://www.tidytextmining.com/tidytext.html 


# Appendices

## Retrieve USPTO patent data
The code chunk for the USPTO acquistion shall be used when documents beyond the Google archive are needed.
```{r a_get_uspto_patent}
# Example https://developer.uspto.gov/ibd-api/v1/patent/application?applicationNumber=US12795356'
# Requires nasa_patents objects

for (app in nasa_patents$Application_SN_uspto) {
  #get_patent_application_uspto(app)
  url <- paste0('https://developer.uspto.gov/ibd-api/v1/patent/application?applicationNumber=',app)
  path <- "data/uspto"
  file_path <- file.path(path, str_c(app, ".html"))
raw.df <- read.csv("data/patent_text.csv", as.is = TRUE)
raw.df$filingDate <- as.Date(raw.df$filingDate, format = "%Y-%m-%d")
}
```

### USPTO
We didn't use the USPTO source. We acquired patent data from Google, instead. This code chunk for this acquistion is disabled because I don't understand what it retrieves, but I'll keep the code in case I can use it later.
```{r get_uspto, eval=FALSE}
# Curl
# curl -X GET --header 'Accept: application/json' 'https://developer.uspto.gov/ibd-api/v1/patent/application?applicationNumber=US14202699%2CUS12795356&start=0&rows=100'
# Request URL
# https://developer.uspto.gov/ibd-api/v1/patent/application?applicationNumber=US14202699%2CUS12795356&start=0&rows=100

  if (!file.exists(file_path)) {
    patent_application <- jsonlite::fromJSON(url)
    #test
    print(patent_application)
    
    #  Bulk download not ideal, disable download from USPTO
    ##download.file(patent_application$response$docs$archiveUrl, file.path(path)) 
    
    #  Instead use the following form to query for new HTML files 
    #  http://patft.uspto.gov/netahtml/PTO/index.html
    #  Example: http://patft.uspto.gov/netacgi/nph-Parser?Sect1=PTO1&Sect2=HITOFF&d=PALL&p=1&u=%2Fnetahtml%2FPTO%2Fsrchnum.htm&r=1&f=G&l=50&s1=5963949.PN.&OS=PN/5963949&RS=PN/5963949
    break
  }
  
}

print("Downloads complete.")
```

## View Patents View Information (for instance, the Abstract)
```{r a_get_patentsview}
library(patentsview) 

retrvble_flds <- get_fields(endpoint = "patents")
head(retrvble_flds)


result <- search_pv(
  query = qry_funs$eq(patent_number = "8293178"),
  fields = get_fields(endpoint = "patents", groups = c("patents", "inventors"))
)

result
result$data$patents$patent_abstract
```

### Google Patents
Other attributes explored
```{r, a_explore_google_patent, eval=FALSE}
# prior art keywords
raw.html %>% html_nodes("[itemprop='priorArtKeywords']") %>% html_text() 
# inventors
raw.html %>% html_nodes("[itemprop='inventor']") %>% html_text()
# current assignee
raw.html %>% html_nodes("[itemprop='assigneeCurrent']") %>% html_text()
# original assignee
#raw.html %>% html_nodes("[itemprop='assigneeOriginal']") %>% html_text() # lots of noise; need to parse later
# filing date
raw.html %>% html_nodes("[itemprop='filingDate']") %>% html_text() # which one to select?
# classifications
raw.html %>% html_nodes("[itemprop='cpcs']") %>% html_text() # what does it mean?
```

### Research papers
Explore PLOS. Commentary in code chunk. Unhide to review.

```{r explore_plos}
# All the fields you can query.
plosfields

# All the journals.
journalnamekey()

# Search for an author. Return the research paper ID and title.
searchplos(q = "author:sulzer", fl = "id, title")

# Query on a keyword. Return ID, date, title, and abstract.
p <- searchplos(q = "synuclein",
                fl = c("id", "publication_date", "title", "abstract"),
                limit = 20)

# The number of hits.
p$meta

# The data.
p$data
```
### Explore one patent at a time
- appId: US6226553B1
- title: US5689004ADiamines containing pendent phenylethynyl groups
- search: Find papers whose body contains the term "phenylethynyl".

```{r explore_one_patent_1}
p <- searchplos(q = "body:phenylethynyl",
                fl = c("id", "publication_date", "title", "abstract"))

# The number of hits.
p$meta

# The data.
p$data
```

- appId: US6261844B1
- title: US5730806AGas-liquid supersonic cleaning and cleaning verification spray system
- search: - search: Find papers whose body contains the term "liquid supersonic cleaning."

```{r explore_one_patent_2}
p <- searchplos(q = "body:liquid supersonic cleaning",
                fl = c("id", "publication_date", "title", "abstract"))

# The number of hits.
p$meta

# The data.
p$data
```

### Title terms
Search for papers whose bodies contain the top words from NASA patent titles.
```{r explore_title_terms}
top_title_words <- title_words %>% top_n(10)
top_title_words <- top_title_words$word

for (word in top_title_words) {
  q <-  paste0("body:", word)
  p <- searchplos(q = q,
                  fl = c("id", "publication_date", "title", "abstract"))
  
  print(paste0("Search term: ", word))
  print(paste0("Count: ", p$meta$numFound))
  print(paste0("Sample of documents found..."))
  print(head(p$data), n = 5)
}
```

## Resources
### Collaboration
- [Work Breakdown Structure](https://docs.google.com/spreadsheets/d/11siAxFAxaqqPvVJ5Qvedzgi_2dRuKNJpJ_qdjGm2p10/edit#gid=999682295).

### References
- [The WIPO Manual on Open Source Patent Analytics](https://wipo-analytics.github.io). An end-to-end guide for information retrieval for patents and research papers.
- [How AI Can Tame the Scientific Literature](https://www.nature.com/articles/d41586-018-06617-5). Survey of Iris.ai, Semantic Scholar from the Allen Institute for Artificial Intelligence, Microsoft Academic, etc. Iris.ai sources CORE.

### Agencies and services
- [WIPO](https://www.wipo.int/portal/en/index.html). The World Intellectual Property Organization.
- [Public Library of Science](https://www.plos.org). PLOS. 200K+ open access peer-reviewed journal articles.
- [CORE](https://core.ac.uk). Claims to be the largest aggregator of open access research papers, with an inventory of 135M+. Provides APIs for text mining.
- [rOpenSci](https://ropensci.org). Non-profit that addresses reproducibility of scientific data retrieval. A raft of R packages for working with scientific data sources and supporting research. Leadership includes Jenny Bryan and advisors include Hadley Wickham. Blog, tutorials, and videos.
- [Allen Institute for Artificial Intelligence](https://allenai.org). Semantic Scholar, etc.
- [One World Analytics](http://oneworldanalytics.com). Analyzes social and environmental issues using text mining, statistics, geographic mapping and network visualisation.

### NASA
- [NASA's Open Data Portal](https://data.nasa.gov).
- [NASA Patents](https://data.nasa.gov/Raw-Data/NASA-Patents/gquh-watm).

### US patent data
- [USPTO Open Data Portal](https://developer.uspto.gov). United States Patent and Trademark Office data products. Bulk downloads, APIs, analytics, etc.
- [PatentsView](http://www.patentsview.org/). Secondary source, with dataset downloads and APIs.

### R packages
- `rplos` [Vignette](https://cran.r-project.org/web/packages/rplos/rplos.pdf). Interface to the Solr based search [API](http://api.plos.org/) for PLOS journals. Functions search for articles, retrieve articles, make plots, do faceted searches, highlight searches, and present results of highlighted searches in a browser.
- `fulltext` [Vignette](https://ropensci.org/tutorials/fulltext_tutorial/). Facilitates text mining with an emphasis on open access journals. The vignette provides examples.

### APIs
- [PLOS API](http://api.plos.org/). Documentation, articles, frequently asked questions.

### Examples
- [PLos Article Classification](https://github.com/akud/PLoS-Article-Classification). A Python project on GitHub using machine learning to classify scientific articles by subject.
- [Open NASA Data from API to Data Analysis](https://www.youtube.com/watch?v=JoaQctLP2Cg). YouTube video by Noemi Derzsy, NASA Datanaut, from the 2017 NYC SpaceApps Conference. Easy introduction to data obtainable from NASA.
- [Mosaic Knowledge Graphs](https://mosaickg.apps.allenai.org). Allen Institute. Graph network analysis of text.
