---
title: "ipsci"
author: "TJ"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_folding: hide
    highlight: pygments
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(rplos)    # API to PLOS for journals.
library(readr)    # Reading rectangular data.
library(plyr)     # Wrangling data.
library(dplyr)    # Wrangling data.
library(tibble)   # Tidier table object.
library(tidyr)    # Tidying data,
library(stringr)  # Manipulating strings. Using RegEx.
library(tm)       # Text mining.
library(fulltext) # Text mining of open access journals.
library(XML)      # Dealing with text in xml.
library(httr)     # Wrapper for the curl package.
library(jsonlite) # Getting and formatting JSON.
```

## NASA Patents
- Data source: [NASA's Open Data Portal](https://data.nasa.gov/Raw-Data/NASA-Patents/gquh-watm). Includes column specification.
- File: NASA_Patents.csv
- Download date: 11/14/2019

### Notes
- Once you determine the data types of your columns,set the specifications and then use them for reading.
- [`readr` blog post](https://blog.rstudio.com/2016/08/05/readr-1-0-0/). Illustrates the approach, although this syntax doesn't work anymore. The approach writes the specification to a file.
- [readr - how to update col_spec object from spec()](https://stackoverflow.com/questions/39135129/readr-how-to-update-col-spec-object-from-spec). Greg H.'s answer on Stack Overflow doesn't require writing to a file. We use this approach. 

```{r nasa}
nasa_patents_fn <- "NASA_Patents.csv"

# Specify datatypes.
nasa_spec <- spec_csv(file = file.path("data", nasa_patents_fn))
nasa_spec$cols[["Status"]] <- col_factor()
nasa_spec$cols[["Patent Expiration Date"]] <- col_date("%m/%d/%Y")

# Read patent file.
nasa_patents <- readr::read_csv(file = file.path("data", nasa_patents_fn),
                                col_types = nasa_spec)

# In variable names, replace spaces.
names(nasa_patents) <- str_replace_all(string = names(nasa_patents),
                                       pattern = " ",
                                       replacement = "_")

# Transform the application number to USPTO format
nasa_patents <- nasa_patents %>%
  mutate(Application_SN_uspto = str_c("US",
        str_replace_all(Application_SN, "[[:punct:]]", "")))
```

## Retrieve patent data
### USPTO
The code chunk for this acquistion is disabled because I don't understand what it retrieves, but I'll keep the code in case I can use it.
```{r get_uspto, eval=FALSE}
# Curl
# curl -X GET --header 'Accept: application/json' 'https://developer.uspto.gov/ibd-api/v1/patent/application?applicationNumber=US14202699%2CUS12795356&start=0&rows=100'
# Request URL
# https://developer.uspto.gov/ibd-api/v1/patent/application?applicationNumber=US14202699%2CUS12795356&start=0&rows=100

get_patent_application_uspto <- function(app_num) {
  file_path <- file.path("data", str_c(app_num, ".json"))
  
  if (!file.exists(file_path)) {
    req_url <- "https://developer.uspto.gov/ibd-api/v1/patent/application?APPSTUB"
    req_url <- str_replace(string = req_url,
                           pattern = "APPSTUB",
                           replacement = as.character(app_num))
    print(req_url)
    print(str_c("Downloading application ",
                as.character(app_num), "..."))
    
    patent_application <- fromJSON(req_url)
    print(patent_application$response)
    #stream_out(x = patent_application[["response"]][["docs"]],
    #           file(file_path))
    
    #print(file_path)
  }
}

# Need to review contents of JSON files.
for (app in nasa_patents$Application_SN_uspto) {
  #get_patent_application_uspto(app)
  patent_application <- fromJSON('https://developer.uspto.gov/ibd-api/v1/patent/application?applicationNumber=US12795356')
  print(patent_application)
  download.file(patent_application$response$docs$archiveUrl, file.path("data")) 
  break
}

print("Downloads complete.")
```

### Google
```{r get_google_patent}
get_patent_google <- function(pat_num) {
  file_path <- file.path("data", str_c(pat_num, ".html"))

  if (!file.exists(file_path)) {
    req_url <- "https://patents.google.com/patent/USPATNUMSTUB"
    req_url <- str_replace(string = req_url,
                           pattern = "PATNUMSTUB",
                           replacement = as.character(pat_num))
    print(str_c("Downloading patent ",
                as.character(pat_num), "..."))
    
    r <- GET(req_url, write_disk(file_path))
    warn_for_status(r)
  }
}

# Filter missing patent numbers
is_na_patnum <- is.na(nasa_patents$Patent_Number)
is_patnum <- nasa_patents$Patent_Number > 0

nasa_patent_numbers <- nasa_patents$Patent_Number[!is_na_patnum & is_patnum]

for (patnum in nasa_patent_numbers) {
   get_patent_google(patnum)
}

print("Downloads complete.")
```


## Try out Patents View

```{r}
library(patentsview)
library(tidyr)

retrvble_flds <- get_fields(endpoint = "patents")
head(retrvble_flds)


# Get patent
#query = qry_funs$eq(patent_number = "8293178")
#query = '{"_gte":{"patent_number":"82931781"}}'

result <- search_pv(
  query = qry_funs$eq(patent_number = "8293178"),
  fields = get_fields(endpoint = "patents", groups = c("patents", "inventors"))
)


#Abstract
result
result$data$patents$patent_abstract


#%>% 
#  tidyr::unnest() %>%
#  head()

```

 

# Try out sample code on patentsview for geo queries

```{r}

# Write a query:
query <- with_qfuns( # with_qfuns is basically just: with(qry_funs, ...)
  and(
    begins(cpc_subgroup_id = 'H04L63/02'),
    gte(patent_year = 2007)
  )
)

# Create a list of fields:
fields <- c(
  c("patent_number", "patent_year"),
  get_fields(endpoint = "patents", groups = c("assignees", "cpcs"))
)

# Send HTTP request to API's server:
pv_res <- search_pv(query = query, fields = fields, all_pages = TRUE)
library(leaflet)
library(htmltools)
library(dplyr)
library(tidyr)

data <-
  pv_res$data$patents %>%
    unnest(assignees) %>%
    select(assignee_id, assignee_organization, patent_number,
           assignee_longitude, assignee_latitude) %>%
    group_by_at(vars(-matches("pat"))) %>%
    mutate(num_pats = n()) %>%
    ungroup() %>%
    select(-patent_number) %>%
    distinct() %>%
    mutate(popup = paste0("<font color='Black'>",
                          htmlEscape(assignee_organization), "<br><br>Patents:",
                          num_pats, "</font>")) %>%
    mutate_at(vars(matches("_l")), as.numeric) %>%
    filter(!is.na(assignee_id))

leaflet(data) %>%
  addProviderTiles(providers$CartoDB.DarkMatterNoLabels) %>%
  addCircleMarkers(lng = ~assignee_longitude, lat = ~assignee_latitude,
                   popup = ~popup, ~sqrt(num_pats), color = "yellow")
```

Ref
https://ropensci.org/blog/2017/09/19/patentsview/
https://www.patentsview.org/web/#viz/locations
https://raw.githubusercontent.com/ropensci/patentsview/483be92df486211bb2e6b54d64d5d7aacef40ab3/inst/site/vignettes/top-assignees.Rmd

## Section beginning Methods


"The tidyverse is an opinionated collection of R packages designed for data science. All packages share an underlying design philosophy, grammar, and data structures."


The core tidyverse:
 *  ggplot2 is a system for declaratively creating graphics, based on The Grammar of Graphics.  
 *  dplyr provides a grammar of data manipulation, providing a consistent set of verbs that solve the most common data manipulation challenges.  
 *  tidyr provides a set of functions that help you get to tidy data.  
 *  readr provides a fast and friendly way to read rectangular data (like csv, tsv, and fwf).  
 *  purrr enhances R’s functional programming (FP) toolkit by providing a complete and consistent set of tools for working with functions and vectors. 
 *  tibble is a modern re-imagining of the data frame, keeping what time has proven to be effective, and throwing out what it has not. Tibbles are data.frames that are lazy and surly.
 *  stringr provides a cohesive set of functions designed to make working with strings as easy as possible.  
 *  forcats provides a suite of useful tools that solve common problems with factors.

More specialised usage or Tidyverse-adjacent:
 *  readr, for reading flat files 
 *  readxl for .xls and .xlsx sheets.
 *  haven for SPSS, Stata, and SAS data.
 *  googledrive package allows you to interact with files on Google Drive from R.
 *  jsonlite for JSON.
 *  xml2 for XML.
 *  httr for web APIs.
 *  rvest for web scraping.
 *  DBI for relational databases. 
 *  lubridate for dates and date-times.
 *  hms for time-of-day values.
 *  blob for storing blob (binary) data. 
 *  magrittr provides the pipe, %>% used throughout the tidyverse. It also provide a number of more specialised piping operators (like %$% and %<>%) that can be useful in other places.
 *  glue provides an alternative to paste() that makes it easier to combine data and strings.
 *  Modelling within the tidyverse is largely a work in progress. This work will largely replace the modelr package used in R4DS.
 *  You may also find broom to be useful: it turns models into tidy data which you can then wrangle and visualise using the tools you already know.


Ref:
TODO: add notes on this section
tidyverse.org
https://rstudio.com/resources/webinars/the-grammar-and-graphics-of-data-science/


## Exploration of raw data
Compare uspto and google (focus on google for now (it is deprecated so may be missing files))
Use html for now, instead of google bigquery api
#>US8293178B2 - Chemochromic detector for sensing gas leakage and process for producing the same 
#https://patents.google.com/patent/US8293178
#http://patft.uspto.gov/netacgi/nph-Parser?Sect1=PTO1&Sect2=HITOFF&d=PALL&p=1&u=%2Fnetahtml%2FPTO%2Fsrchnum.htm&r=1&f=G&l=50&s1=8293178.PN.&OS=PN/8293178&RS=PN/8293178 (a link explaining the quality of patentsview, uspto, and google patent capabilities and information outlining the uspot full text API is here https://developer.uspto.gov/api-catalog/patentsview -- TODO: add to FAQ)

```{r}
library(rvest)
html_u <- read_html(file.path("data", "paft_uspto_8293178.html"))
html_g <- read_html(file.path("data", "8293178.html"))
html_g
```

```{r}
library(magrittr) #for pipes
library(dplyr) #for pull function
library(rvest) #get html nodes
library(xml2) #pull html data
library(selectr) #for xpath element
library(tibble)
library(purrr) #for map functions
library(datapasta) #for recreating tibble's with ease
#Sample Data
sample_data <- tibble::tibble(
  name = c("test"),
  link = c("https://patents.google.com/patent/US8293178"
  )
)
```

 
https://towardsdatascience.com/functions-with-r-and-rvest-a-laymens-guide-acda42325a77
### Tests
```{r}
title <- html_g %>%
        html_nodes("h1") %>%
        html_text()
title
claim <- html_g %>% html_nodes("div.claim") 
claim
divs <- html_g %>%
        html_nodes('div') %>% 
        html_text()
```


```{r} 
library(tidytext) 
library(tidyr)
library(stringr)



section_nodes <- html_g %>% html_nodes("section")

head(section_nodes)

section_ids <- section_nodes %>% html_attr("itemprop") 
#section_ids <- html_g %>% html_nodes(xpath="section//h2")
section_ids


#https://stackoverflow.com/questions/43598427/r-how-to-extract-items-from-xml-nodeset
#number=rep(1: (section_nodes)),

text_df <- tibble(section_ids=section_ids, text=sections_text)

text_df


```

```{r}


#TODO: combine
sections_text <- section_nodes %>% 
    html_text() %>% 
    str_trim(side = "both") %>%
    str_replace_all('(\\s){2,}', '\\1') %>% 
    str_replace_all('(\\r\\n|\\n){2}', '\\1')
    #substr(start = nchar(body_text)-700, stop = nchar(body_text))
#        strsplit(split = "\n") %>%
#        unlist() %>%
#        .[. != ""]
sections_text

```


 


Ref:
idea, use nasa highlights via tesseract to analyze https://www.techbriefs.com/dl/HOT100/MonSys.pdf
option, do a 1 level crawl into cited by or related patents https://patents.google.com/patent/US7383238B1/en#citedBy
html_node basics https://bradleyboehmke.github.io/2015/12/scraping-html-text.html
uspto html structure ideas https://en.wikipedia.org/wiki/User:Jrincayc/Patent_utils
another option for patent search https://cloud.google.com/blog/products/gcp/google-patents-public-datasets-connecting-public-paid-and-private-patent-data
patentsview (todo: put research here)

 
 
More tidy http://vita.had.co.nz/papers/tidy-data.pdf
Advanced:
https://rddj.info/
https://cloud.r-project.org/web/packages/hunspell/vignettes/intro.html
https://juliasilge.com/blog/life-changing-magic/
https://rud.is/projects/clinton_emails_01.html







## Just some notes

```{r}
require("devtools")
#install_github("tidymodels/textrecipes")

```






```{r}
library(recipes)
library(textrecipes)

data(okc_text)
o<-data(okc_text)
okc_rec <- recipe(~ ., data = okc_text) %>%
  step_tokenize(essay0, essay1)
okc_text
```


```{r}
okc_rec <- recipe(~ ., data = okc_text) %>%
  step_tokenize(essay0, essay1) %>% # Tokenizes to words by default
  step_stopwords(essay0, essay1) %>% # Uses the english snowball list by default
  step_tokenfilter(essay0, essay1, max_tokens = 100) %>%
  step_tfidf(essay0, essay1)
   
okc_obj <- okc_rec %>%
  prep(training = okc_text)
   
str(bake(okc_obj, okc_text), list.len = 15)
```

```{r}
recipe(~ ., data = data) %>%
  step_tokenize(text) %>%
  step_stem(text) %>%
  step_stopwords(text) %>%
  step_topwords(text) %>%
  step_tf(text)

# or

recipe(~ ., data = data) %>%
  step_tokenize(text) %>%
  step_stem(text) %>%
  step_tfidf(text)
```
Ref:
https://tidymodels.github.io/textrecipes/
https://tidymodels.github.io/textrecipes/articles/cookbook---using-more-complex-recipes-involving-text.html

gganimate extends the grammar of graphics as implemented by ggplot2 to include the description of animation. It does this by providing a range of new grammar classes that can be added to the plot object in order to customise how it should change with time.

Also https://www.tidyverse.org/blog/2019/07/ragg-0-1-0/

More ideas on innovation https://www.patentsview.org/web/#viz/comparisons&cmp=all/state/numDesc/2019
```{r}

```

