---
title: "ipsci - Abstract Analysis Presentation Review"
author: "Jai Jeffryes, Tamiko Jenkins, Nicholas Chung"
date: "12/14/2019"
output: 
  html_document:
    code_folding: hide
    highlight: pygments
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, message=FALSE}
# Packages used in the ingestion of data 
library(readr)        # Reading rectangular data 

# Packages used for special use cases 
library(topicmodels)  # for LDA topic modelling 
library(SnowballC)    # for stemming
library(tidyverse)    # general utility & workflow functions 
library(tidytext)     # text analysis in R 
library(lubridate)    # working with times and dates   
library(rvest)        # Download and manipulate HTML

# Packages used to prettify and produce visualizations
library(kableExtra)   # tables
library(ggplot2)      # graphs library 
```

# Text Analysis 

## View Data
Examine the patent text files and view the text sections. We note 932 observations, 8 variables, and 2 integer classes and 6 character classes. 
```{r view}
patents <- read.csv("data/patent_text.csv", header = TRUE, stringsAsFactors = FALSE)
glimpse(patents)
head(patents, n=2)
```

## Data integrity
Check to make sure we are not operating on empty data. We are not. 
```{r integrity}
nrow(patents) == sum(complete.cases(patents))
```

Track our documents in case we need to make extra rows for each word
```{r Track}
#patents <- patents %>%    
  #mutate(docId=as.integer(row.names(.)))
`%notin%` <- Negate(`%in%`)
if('docId' %notin% colnames(patents)) patents<-add_column(patents, docId=as.integer(row.names(patents)), .before = 1)
head(patents, n=1)
```
 
## Transformations

### Remove third-party additions to text
```{r third}
head(patents$title, n=1)
patents <- patents %>%
  #head(n=1) %>%
  mutate(title = str_remove_all(title, " - Google Patents"))
head(patents$title, n=1)
```


### Clean
```{r clean}
patents <- patents %>%
  mutate(title=iconv(title, to='ASCII//TRANSLIT')) %>%
  mutate(title=tolower(title)) %>%
  mutate(title=str_replace_all(title,'\\w*\\d\\w*','')) %>%
  mutate(title=str_replace_all(title,'\\b(apparatus|article|control|device|includ.*|provid*|methods*|system*)\\b','')) %>%
  mutate(abstract=iconv(abstract, to='ASCII//TRANSLIT')) %>%
  mutate(abstract=tolower(abstract)) %>%
  mutate(abstract=str_replace_all(abstract,'\\w*\\d\\w*','')) %>%
  mutate(abstract=str_replace_all(abstract,'\\b(apparatus|article|control|device|includ.*|provid*|methods*|system*)\\b','')) %>%
  mutate_if(is.character, str_squish)
head(patents, n=2)
```



### Word operations
```{r words, message=FALSE}
tb_abstracts <- patents %>%
  select(., c(docId, abstract)) %>%
  as_tibble() %>%
  unnest_tokens(word, abstract) %>%
  anti_join(stop_words)
head(tb_abstracts, 10)
```

### Stop words and Tokenization

```{r tokens}
tb_abstracts <- patents %>%
  select(., c(docId, abstract)) %>%
  as_tibble() %>%
  unnest_tokens(word, abstract) %>%
  anti_join(stop_words)
head(tb_abstracts, 10)
```

### Document Term Matrix

```{r counts}
abstract_word_counts <- tb_abstracts %>%
  count(docId, word, sort = TRUE)%>%
  ungroup()

head(abstract_word_counts %>% arrange(docId) %>% group_by(docId) %>% filter(n==max(n)) %>% ungroup(), 10)
```


```{r dtm}
abstract_dtm <- abstract_word_counts %>%
  cast_dtm(docId, word, n)

abstract_dtm
```

### LDA Model

```{r lda}
abstract_lda <- LDA(abstract_dtm, k = 60, control = list(seed = 1234))
abstract_lda
```

 
#### Beta of Top Term per Topic
```{r beta}
topic_beta <- tidy(abstract_lda, matrix = "beta")
#head(topic_beta) %>% arrange(topic, -beta)

top_terms <- topic_beta %>%
  group_by(topic) %>%
  top_n(1, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)
top_terms

```

#### Gamma of Top Topic per Document

```{r gamma}
topic_gamma <- tidy(abstract_lda, matrix = "gamma")
topic_gamma$document <- as.integer(topic_gamma$document)
#topic_gamma %>% arrange(document,desc(gamma)) %>%   head(5)
 

term_document <- topic_gamma %>% 
  group_by(document) %>%
  top_n(1, gamma) %>%
  ungroup() %>%
  arrange(document, gamma)

term_document
```



### Summarize Data

#### Join patents by document ids, topic gammas, term betas, and td_ifd
```{r join}
topic_terms <- inner_join(term_document, top_terms, by = "topic") 
topic_terms <- topic_terms %>% rename(docId=document)

patent_topics <- merge(patents, topic_terms, by = "docId")  
#head(patent_topics)


summary <- patent_topics %>% select(docId, topic, gamma, term, beta, abstract, citedBy, citations)

#head(summary)
 
abstracts_tf_idf <- tb_abstracts %>% 
  count(docId, word, sort = TRUE) %>%
  ungroup() %>%
  bind_tf_idf(word, docId, n) 

doc_abs_tf_idf <- abstracts_tf_idf %>%
  group_by(docId) %>% 
  filter(tf_idf == max(tf_idf)) %>% 
  slice(1) %>% 
  ungroup() 

#head(doc_abs_tf_idf)
 
summary <- doc_abs_tf_idf %>% rename(td_idf_word=word, raw_freq=n) %>% 
  merge(summary, .) %>% 
  select(., -c(abstract, citedBy, citations), c(abstract, citations, citedBy))
  
#head(summary)
```


### Extract
```{r extract}
write.csv(summary,"data/patent_abstract_summary.csv")
```


## Visualize


### Frequency

#### Corpus Word Frequency

```{r corpus-wf, warning=FALSE, message=FALSE}

corpus_word_counts <- tb_abstracts %>%
  count(word, sort = TRUE)  

corpus_word_counts %>% 
  top_n(10, n) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill=word)) +
  geom_col() +
  xlab(NULL) +
  ylab("Word Frequency") +
  ggtitle("Corpus Word Frequency") +
  coord_flip() +
  guides(fill = guide_legend(reverse=TRUE)) 

head(corpus_word_counts,n=2)
 
```


 
#### Document Word Frequency

```{r abstract-wf}
filter_abstract_word_counts <- tb_abstracts %>%
  count(docId, word, sort = TRUE)  %>%   
  group_by(docId) %>%
  arrange(docId, n) %>%   
  slice(1:5)  %>% 
  ungroup()


filter_abstract_word_counts[11:19,]
 
```


  

```{r filter-wc}
filter_abstract_word_counts %>%  
  filter(docId<6) %>%
  ggplot(aes(word, n, fill = as.factor(docId))) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  scale_x_reordered() +
  labs(title = "Document Word Frequency",
       x = NULL, y = expression(n)) +
  facet_wrap(~ docId, ncol = 4, scales = "free")
 

```


### LDA

#### Corpus LDA Terms per Topic

```{r lda-vis, messages=FALSE}
tidy_abstract_lda <- tidy(abstract_lda)
 

filter_tidy_abstract_lda <- tidy_abstract_lda %>% 
  arrange(topic, desc(beta)) %>%
  group_by(topic) %>% 
  filter(topic<6) %>%
  top_n(5) %>%
  ungroup() 
  
filter_tidy_abstract_lda %>%
  mutate(topic = as.factor(topic),
         term = fct_reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = topic)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~topic, ncol=3, scales = "free") +
  coord_flip() + 
  scale_x_reordered() +
  labs(y =  expression(beta),
       x = NULL,
       title = "Corpus LDA terms per topic")

 

head(filter_tidy_abstract_lda, n=2)
```
 



#### Top Document LDA Terms
```{r lda-doc-vis}
topic_beta <- tidy(abstract_lda, matrix = "beta")
#head(topic_beta) %>% arrange(topic, beta)
 
top_terms <- topic_beta %>%
  group_by(topic) %>%
  top_n(1, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)
#top_terms

topic_gamma <- tidy(abstract_lda, matrix = "gamma") 
#topic_gamma %>% arrange(document,desc(gamma)) %>%   head(5)
 
 
term_document <- topic_gamma %>% 
  mutate(docId = as.integer(topic_gamma$document)) %>%
  group_by(docId) %>%
  top_n(5, gamma) %>%
  filter(docId<6) %>%
  ungroup() %>%
  arrange(docId,- gamma)

#term_document

topic_terms_doc <- inner_join(term_document, top_terms, by = "topic")


  
topic_terms_doc %>%
  mutate(docId = as.factor(document),
         term = fct_reorder(term, gamma)) %>%
  ggplot(aes(term, gamma, fill = document)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~document, ncol=3, scales = "free") +
  coord_flip() + 
  scale_x_reordered() +
  labs(y =  expression(gamma),
       x = NULL,
       title = "Top Document LDA Terms")


head(topic_terms_doc, n=3)
```


#### Top Document TD-IDF Terms

```{r tdidf-vis} 
filter_abstracts_tf_idf <- abstracts_tf_idf %>% 
  arrange(docId, desc(n)) %>%
  group_by(docId) %>% 
  filter(docId<6) %>%
  top_n(5) %>%
  ungroup()
   

  
filter_abstracts_tf_idf %>%
  mutate(docId = as.factor(docId),
         term = fct_reorder(word, n)) %>%
  ggplot(aes(term, n, fill = docId)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~docId, ncol=3, scales = "free") +
  coord_flip() + 
  scale_x_reordered() +
  labs(y =  expression(n),
       x = NULL,
       title = "Top Document TD-IDF Terms")
```




## Review


```{r review-sum, out.width="100%"}
head(summary, n=5) %>%
  select(abstract, everything()) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, width = "50em")   

```


### Session info
```{r session}
sessionInfo(package = NULL)
```

